Mg Depleted and K Enriched Stars from LAMOST Spectral Data

### 2018-01-10 article/ms.tex
additional csv files for purposes of code running, plus super shitty abstract

% Abstract of the paper
\begin{abstract}

\end{abstract}

>>>>

% Abstract of the paper
\begin{abstract}
454180 RGB stars from the low resolution LAMOST dr2 survey are searched for anomalously high K and depleted Mg signatures. These LAMOST stars are overwhelmingly field stars, making this the largest search for field stars containing the Mg-K anti-correlation so far identified only in the globular NGC 2419 and NGC 2808. 23 stars displaying absorption spectra with over-abundant K and depleted Mg accross a range of metalicities relative to typical Milky Way field stars, but none are identified as having abundances consistent with the extreme abundances found in NGC 2419. The abundances are in these 23 stars are estimated at ranging between [INSERT RANGE FOR K AND MG HERE]. High resolution spectra for three stars (1 of which is not included among the final count of 23 spectral candidates for the signiature for reasons relating to the LAMOST signal quality for that star, despite having the highest K abundance of the three at [K/Fe]~1.54) selected based on observability were obtained using Las Campanas Observatory, and for these stars elemental abundances for heavy elements such as Sc and V are presented as well as more precise abundances for Mg and K.
\end{abstract}
